
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 10: Predictive Modeling - Part 1"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment10.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Use the `Adult Census Income` dataset.  We will predict the income (whether or not it is more than 50k or not) of an adult. Import the dataset.  Partition the data into 80% training and 20% testing.  
```{r}
library(tidyverse)
library(ggplot2)
library(caret)
setwd("C:/Users/student/Documents/Stat Analysis with R/MATH421")
df <- read_csv('adult_census.csv')
df = drop_na(df)
df <- df %>% 
  mutate(income = as.factor(income), workclass = as.factor(workclass),
         education = as.factor(education),
         marital.status = as.factor(marital.status),
         occupation = as.factor(occupation), relationship = as.factor(relationship), race = as.factor(race), sex = as.factor(sex), native.country = as.factor(native.country)
         )

splitIndex <- createDataPartition(df$income, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```


2. Practice Decision Tree.  Do the follows:

  - Use `rpart` package, create a decision tree with maximum depth of 3. 
```{r}
library(rpart)
tree_model <- rpart(income ~ ., data = df_train,
                 control = rpart.control(maxdepth = 3))
```
  
  - Calculate the accuracy of the model on the testing data. Notice that the positive outcome here is not `1` but `>50K` or `<50K`. 
```{r}
pred <- predict(tree_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall

```
  
  - Plot the tree
```{r}
library(rattle)
fancyRpartPlot(tree_model)
```
  
  
  - Plot the variable importance by the tree
```{r}
tree_model$variable.importance
barplot(tree_model$variable.importance)
```
  
3. Create 3 more trees and compare the testing accuracy of these trees, which tree give the highest testing accuracy.
```{r}
tree_model <- rpart(income ~ ., data = df_train,
                 control = rpart.control(maxdepth = 2))
pred <- predict(tree_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```
```{r}
tree_model <- rpart(income ~ ., data = df_train,
                 control = rpart.control(maxdepth = 4))
pred <- predict(tree_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```
```{r}
tree_model <- rpart(income ~ ., data = df_train,
                 control = rpart.control(maxdepth = 5))
pred <- predict(tree_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```


4. Practice Random Forest.  Do the follows: 

  - Use `randomForest` package, create a random forest of 1000 trees. 
```{r}
library(randomForest)
forest_model = randomForest(income ~ ., data=df_train, ntree = 1000)
```
  
  - Calculate the accuracy of the model on the testing data. 
```{r}
pred <- predict(forest_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```
  
  - Plot the variable importance by the forest
```{r}
importance(forest_model)
barplot(head(importance(forest_model)))
```

5. Create 3 more forests and compare the testing accuracy of these forests, which forest give the highest testing accuracy.
```{r}
library(randomForest)
forest_model = randomForest(income ~ ., data=df_train, ntree = 250)
pred <- predict(forest_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```
```{r}
library(randomForest)
forest_model = randomForest(income ~ ., data=df_train, ntree = 500)
pred <- predict(forest_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```
```{r}
library(randomForest)
forest_model = randomForest(income ~ ., data=df_train, ntree = 750)
pred <- predict(forest_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$income)
cm$overall
```


6. What is the best model (in term of testing accuracy) among all models (including trees and forests) you have trained?

```{r}
'Overall, the best model in terms of testing accuary is the random forest with 750 trees. It has an accuracy of 0.8727. The random forest with 500 trees was a close second. Increasing the max depth of the decision tree from 3 to 4 and 4 to 5 did not impact the accuracy since a max depth of 3 was the optimal tree.'
```

